Go Implementation of Up-To Techniques for Equivalence of Weighted Languages

### 2020-10-01 paper/paper.tex
badly working partition refinement algorithm

\begin{abstract}
Weighted automata generalize non-deterministic automata by adding
a quantity expressing the weight (or probability) of the execution of each transition.
In this work we propose an implementation of two algorithms for computing language 
equivalence in finite state weighted automata (WAs). The first, a
linear partition refinement algorithm, calculates the largest linear weighted bisimulation
for any given LWA (Linear Weighted Automaton) through an iterative method, 
the second algorithm checks the language equivalence 
of two vectors (states) for a given weighted automata by using an additional
data structure representing a congruence relationship between states.
We then compare the two algorithms results to verify their correctness
on randomly generated automata samples, and provide some runtime statistics.

\end{abstract}

@@

The algorithm is defined by the iterative method:
\begin{eqnarray}
  R_0 = \mker{o}^0, & \quad & R_{i+1} = R_i + \sum_{a \in A} t_a(R_i)^t \label{back} 
\end{eqnarray}
Where $\mker{o}^0$ is an annihilator.
The algorithm stops when $R_{j+1} = R_j$. Proof is available in section 4.2 of \cite{BONCHI201277}

>>>>

\begin{abstract}
Weighted automata generalize non-deterministic automata by adding
a quantity expressing the weight (or probability) of the execution of each transition.
In this work we propose an implementation of two algorithms for computing language 
equivalence in finite state weighted automata (WAs). The first, a
linear partition refinement algorithm, calculates the largest linear weighted bisimulation
for any given LWA (Linear Weighted Automaton) through an iterative method, 
the second algorithm checks the language equivalence 
of two vectors (states) for a given weighted automata by using an additional
data structure representing a congruence relation between states.
We then compare results of the two algorithms to verify their correctness
and performance on randomly generated samples. 
We finally provide comparison of runtime statistics and suggest 
which of the two algorithm is a the best choice for some usage cases.
\end{abstract}

@@

The algorithm is defined by the iterative method:
\begin{eqnarray}
  R_0 = \mker{o}^0, & \quad & R_{i+1} = R_i + \sum_{a \in A} t_a^t(R_i) \label{back} 
\end{eqnarray}
Where $\mker{o}^0$ is an annihilator.
The algorithm stops when $R_{j+1} = R_j$. Proof is available in section 4.2 of \cite{BONCHI201277}
